\Huge Handwritten digit recognition

### 2017-02-09 doc/Paper.tex

\newpage
\section{Introduction}
\TODO{more here}

@@

\begin{align}
y = softmax(Wx + b) \\
image\_label &= argmax(y)
\end{align}

@@

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Time per epoch},
  xlabel=Processes,
  ylabel=Seconds,
  bar width=.8cm,
  axis line style={black!65, line width=.1pt}, % thinner border
  symbolic x coords={1,2,4,6,8,12,16}, % equidistant bars
  every x tick/.style={white}, % hide x ticks (make them white)
  every y tick/.style={line width=.1pt, draw=gray!10}, % y ticks same color as grid
  ymajorgrids=true, % show horizontal grid lines
  grid style={line width=.1pt, draw=gray!10}, % gray grid lines
  ]
  \addplot[ybar, black!40, fill=black!20] coordinates {
      (1,8) 
      (2,5)
      (4,4) 
      (6,3) 
      (8,2.5) 
      (12,2) 
      (16,1.5)    
      };
\end{axis}
\end{tikzpicture}
\end{center}

>>>>

\newpage
\section{Introduction}
Proiectul are ca scop evidentierea rolului paralelismului in programare. Avand vedere cantitatea mare de date cu care se confrunta aplicatiile din ziua de astazi, este nevoie ca acestea sa ruleze anumite sarcini concomitent. Pentru a sublinia imbunatatirile aduse de paralelism, s-a implementat in MPI antrenarea unei retele neuronale. In continuare se vor detalia, datele folosite in model, reteaua construita, metodele de paralelism, rezultatele, dar si interfata.

@@

\begin{align}
y &= softmax(Wx + b) \\
label &= argmax(y)
\end{align}

@@

\begin{center}
\begin{tikzpicture}
\begin{axis}[
  title={Time per epoch},
  xlabel=Processes,
  ylabel=Seconds,
  bar width=1cm,
  enlarge x limits=0.2,
%   enlarge y limits=0.18,
  axis line style={black!65, line width=.1pt}, % thinner border
  symbolic x coords={1,2,4,8,16}, % equidistant bars
  every x tick/.style={white}, % hide x ticks (make them white)
  every y tick/.style={line width=.1pt, draw=gray!10}, % y ticks same color as grid
  ymajorgrids=true, % show horizontal grid lines
  grid style={line width=.1pt, draw=gray!20}, % gray grid lines
  ]
  \addplot[ybar, black!40, fill=black!20] coordinates {
      (1,5.27) 
      (2,2.81)
      (4,1.51)
      (8,0.78)
      (16,0.79)
      };
\end{axis}
\end{tikzpicture}
\end{center}

\noindent The benchmarks were done on the MNIST training set of 60 000 images with a batch size of 1000, on a machine with 20 processors @ 2.60GHz.

The training time is almost halved when going from one (5.27s) to two (2.81s) processors: 88\% improvement. Further 86\% improvement is achieved on four processors (1.51s), less than a third (29\%) of the single-process time. Doubling the number of processes to eight yields a further 94\% improvement (0.78s), making it only 15\% of the single-process time. This is notable when considering the perfect improvement possible of 12.5\%.

For more than eight cores, the communication overhead starts to take its toll. No further performance improvement is achieved. Chunk sizes get increasingly small (1000, 500, 250, 125, 63), hitting an inflection point at the eight-processes mark.
